---
title: "An example data cleaning from raw to processed data"
author: "Marton Kovacs"
date: '2020.04.28 '
output: html_document
---

# Loading packages

```{r}
library(tidyverse)
library(skimr)
```

# Import custom

```{r}
source("utils.R")
```

# Importing data

```{r}
raw <- read_tsv("data/raw/primeprobe_data.tsv")
```

# Filtering rules

* Excluding practice trials
* Excluding participants outside of the 18-99 age range
* Excluding not correct trials

# Exploring data

Checking the column names.

```{r}
colnames(raw)
```

Checking the summary of the age variable.

```{r}
raw %>% 
  select(age) %>% 
  skim()
```

Check if all the participants have the correct number of pratice and test trials.

** practice = 24
** test = 388
** total = 412

```{r}
raw %>% 
  group_by(participant_id) %>% 
  count() %>%
  mutate(complete = case_when(n == 412 ~ "complete",
                              TRUE ~ "incomplete")) %>% 
  group_by(complete) %>% 
  count()
```

# Creating new variables

Create variable for storing whether a response was correct or not.

```{r}
raw <-
  raw %>% 
  mutate(isCorrect = case_when(responseTarget == responseContent ~ 1L,
                               responseTarget != responseContent ~ 0L,
                               TRUE ~ NA_integer_))
```

Create a vaiable for storing the congruency of the previous trial.

```{r}
raw <-
  raw %>%
  mutate(isPrevCongruent = case_when(trialId < 24 ~ NA_integer_,
                                     trialId > 24 & lag(isCongruent) == 1L ~ 1L,
                                     trialId > 24 & lag(isCongruent) == 0L ~ 0L))
```

Create response time variable.

```{r}
raw <-
  raw %>% 
  mutate(rt = case_when(responseContent != "TIMEOUT" ~ responseTime - probeOnset,
                        responseContent == "TIMEOUT" ~ NA_real_))
```

# Filtering

Excluding participants outside of our age range.

```{r}
raw <-
  raw %>%
  mutate(ageDrop = case_when(age < 18 ~ 1L,
                             age > 99 ~ 1L,
                             TRUE ~ 0L)) %>% 
  filter(ageDrop != 1L)
```

Excluding practice trials.

```{r}
raw <-
  raw %>%
  filter(isPractice == 0L)
```

Excluding incorrect trials.

```{r}
raw <-
  raw %>%
  filter(isCorrect == 1L)
```

Exclude participants with incomplete trial numbers.

```{r}
raw <-
  raw %>%
  filter(participant_id %ni% c(381, 392))
```

Exclude first trials.

```{r}
raw <-
  raw %>%
  filter(trialId != 24L)
```

# Figures

```{r}
# Prepare data for plotting
cse_plot_rt_data <- 
  raw %>% 
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Incongruent",
                                     isPrevCongruent ==  1L ~ "Congruent"),
         isCongruent = case_when(isCongruent ==  0L ~ "Incongruent",
                                 isCongruent ==  1L ~ "Congruent")) %>%
  group_by(participant_id, isPrevCongruent, isCongruent) %>% 
  summarise(participant_mean_rt = mean(rt, na.rm = T)) %>% 
  group_by(isPrevCongruent, isCongruent) %>% 
  summarise(N = n(),
            mean_rt = mean(participant_mean_rt, na.rm = T),
            sd_rt = sd(participant_mean_rt, na.rm = T),
            se_rt = sd_rt / sqrt(N))

# Create the plot
cse_plot_rt <- 
  cse_plot_rt_data %>% 
  ggplot() +
  aes(x = isPrevCongruent,
                 y = mean_rt,
                 shape = isCongruent,
                 group = isCongruent) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_rt - se_rt,
                    ymax = mean_rt + se_rt),
                width = .1) +
  scale_shape_manual(values = c(4, 16)) +
  scale_x_discrete(expand = c(1, 0)) +
  xlab("Congruency of the previous trial")+
  ylab("Reaction time") +
  guides(shape = guide_legend(title = "Congruency of \n the current trial")) +
  papaja::theme_apa() +
  theme(legend.position = c(0.85, 0.5),
        axis.line = element_line(color = "black"))

# See the plot
cse_plot_rt
```

## Saving the figure

```{r}
ggsave("figures/rt_cse.png", width = 14.4, height = 8, plot = last_plot())
```